% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document}
\name{Ryan O'Donnell} 
\address{265  Main Road, Montville, NJ 07045 - 862-345-8316}
\address{github.com/odonnellryan - odonnellryanc@gmail.com}

\begin{resume}
 
\section{OBJECTIVE}	A position in a field of programming with focus 
	on web application development and web stack configuration.
 
\section{EDUCATION} {\sl Associates of Science,} Computer Science \\
		County College of Morris, Randolph, NJ  \\
	 	Minor: Business Administration \\ \\
	{\sl CCENT,} Certificate \\
		After successful completion of CCNA and CCNP courses. \\ \\
	{\sl Software Engineering,} Certificate \\
		Harvard Extension School \\
		Expected Completion: Summer 2015

\section{COMPUTER \\ SKILLS} {\sl Languages \& Software:} Python, Go, JavaScript, 
	Nginx, Apache, MySQL, Docker, MongoDB, CSS, HTML, PHP,
	Pycharm, IntelliJ IDEA, Emacs, Sublime, Linux Shell, PowerShell. \\
	{\sl Operating Systems:} Linux, Windows, IOS.

\section{EXPERIENCE} {\sl Lead System Analyst} \hfill Summer 2012 \\
	BMT Corp, Networking and Computer Services Department, Fairfield, NJ
	\begin{itemize}  \itemsep -2pt
		\item Lead the services department successfully while using programming skills to improve
			workflows and tools used by the department. 
		\item Ran status and service reports for a large range of clients including top-50
			London companies consisting of over 2,500 supported users.
		\item   Developed tools to automate many service tasks on windows and linux servers.
	\end{itemize}

	{\sl Hardware Technician} \hfill            Summer 2008 - Summer 2009 \\
	Hardware Repair Department, VideoGame911, Denville, NJ
	\begin{itemize}  \itemsep -2pt
		\item Lead team to develop a customer service portal. 
		\item Used hardware knowledge and skills to repair videogame systems. 
		\item Kept organized records of all repairs. 
	\end{itemize} 

\section{AVAILABILITY}
	Available as soon as proper notice can be given to current employer.

\section {SALARY}
	Salary requirements depend on position and benefits offered.

\section{PROFESSIONAL \\ REFERENCES}
	{\sl George Hoffman - Retired } \\
	261 Main Road Montville NJ \\
	201-486-6864
 
	{\sl Walter White - Retired } \\
	12 Abbet Lane Montville NJ \\
	201-787-6038 

	{\sl Additional Upon Request}

\end{resume}
\end{document}







